### 2022-05-06 manuscript.Rmd
equations and directories fix

@@

Furthermore, the sampling variance was computed according to the following equation:

$sigma$between group = dfdf -2 2ñ1 + g2ñ2- g2J2

Where ñ is the harmonic mean of the group sizes and ñ = nmale nmalenfemale + nmale.
A sensitivity analysis reported in supplementary xxx highlights the stability of the effect size computed using the Bayesian meta analysis.

>>>>

+-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
| Available statistics                                                  | Conversion to standardized mean difference (Hedges' $g$)                             |
+=======================================================================+======================================================================================+
| (1) Cohen's $d$ and group sample size $n$                             | $df=n_{female}+ n_{male}-1$; \quad                                                   |
| [@goulet-pelletier2018; @hedges1985]                                  | $j=\frac{\Gamma(\frac{1}{2}df)}{\sqrt{\frac{df}{2}}\Gamma(\frac{1}{2}(df-1))}$;\quad |
|                                                                       | $g=d*j$                                                                              |
+-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
| (2) $t$-statistic and group sample size $n$                           | $d = t \sqrt{\frac{1}{n_{female}} + \frac{1}{n_{male}$;\quad                         |
| [@lankens2013]                                                        | then (1)                                                                             |
+-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
| (3) $F$ statistic and group sample size                               | $d = \sqrt{f} \sqrt{\frac{1}{n_{female}} + \frac{1}{n_{male}$;\quad                  |
| [@lakens2013]                                                         | then (1)                                                                             |
+-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
| (4) Mean difference in looking times per group + $SD$s                | $SD_\text{mean} = \sqrt{\frac{{(n_{female} - 1) \sigma^2_{female} + (n_{male} -1) \sigma^2_{male}}}{df}}$;\quad |
| [@lankens2013]                                                        | $d=\frac{m_\text{female}-m_\text{male}}{SD_\text{mean}}$;\quad                       |
|                                                                       | then (1)                                                                             |
+-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+
| (5) Mean novelty preference score $m_\text{pref}$ + $SD_\text{pref}$  | $SD_\text{pref} = \sqrt{\frac{{(n_{female} - 1) \sigma^2_{female} + (n_{male} -1) \sigma^2_{male}}}{df}}$;\quad |
|  [@lakens2013]                                                        | $d=\frac{m_\text{female}-m_\text{male}}{SD_\text{pref}}$;\quad                       |
|                                                                       | then (1)                                                                             |
+-----------------------------------------------------------------------+--------------------------------------------------------------------------------------+

@@

Furthermore, the sampling variance was computed according to the following equation:
$    \sigma_{between group} = \sqrt{\frac{df}{df-2} \frac{2}{\tilde{n}} (1 + g^2\frac{\tilde{n}}{2}) - frac{g^2}{J^2}}          $
Where ñ is the harmonic mean of the group sizes and $ñ = \frac{n_{female} n_{male}}{n_{female} + n_{male}}$ and $df$ are given by the equation in Table xxx.
A sensitivity analysis reported in supplementary xxx highlights the stability of the effect size computed using the Bayesian meta analysis.
